---
title: "The Contents of My Package"
author: "Thomas Hernandez"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The Contents of My Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 10,
  fig.height = 6,
  out.width = "90%"
)
```

```{r setup}
library(MATH4753F25thomas)
```

# Link to GITHUB

[Thomas Hernandez's R Package for MATH-4753](https://github.com/thomasfh99/MATH4753F25thomas.git)



# Package Summary

>This vignette shows a few of the functions and a data set that exists within this package. However, there are numerous functions and data sets that are available to use in this package that can be utilized in projects. For example, if I want to use a binomial simulation, I would use the `mybin()` function. Another example: If I want to use the FIREDAM.csv, but not having to import it to the project, I could reference it from my package, and it will still bring in the data from the data without having the .csv file in the root project folder.



# Four Working Functions

## `myboot2()`

>**Description:** This is a mean bootstrap function using a normal distribution where the $n$ sample size of 10, $\mu$ mean of 5, and a $\sigma$ standard deviation of 2.

```{r}
set.seed(68)
sam=rnorm(10,mean=5,sd=2)
myboot2(iter=10000, x=sam, fun="mean", alpha=0.05, xlab="mean", col="#0f20db")
```

## `mybin()`

>**Description:** This is a binomial bar plot showing the binomial probability ($p=0.7$) for the number of successes ($n=10$), all throughout 10000 iterations.

```{r}
mybin(iter=10000, n=10, p=0.7)
```

## `mycltb()`

>**Description:** This is a plot of a Central Limit Theorem (CLT) Binomial Distribution with a binomial probability $p=0.7$ and a sample size of $n=10$, all throughout 10000 iterations.

```{r}
mycltb(n=10, iter=10000, p=0.3)
```

## `myncurve()`

>**Description:** This is a plot of a normal density curve that shades the area (probability) under the curve where $x \leq 6$. The conditions of the curve are where $\mu=10$ and $\sigma=5$.

```{r}
myncurve(mu=10, sigma=5, a=6)
```



# Data Set: FIREDAM.csv

>**Description:** This data set contains information about each fire incident. The two variables are DISTANCE, which shows how far the fire is located from a fire station in miles, and DAMAGE, which shows the amount of thousands of dollars.  

```{r}
# Displays the first six rows of the FIREDAM.csv data set
head(fire)

# Displays the last six rows of the FIREDAM.csv data set
tail(fire)

# Shows a statistical summary of each item in the FIREDAM.csv data set
summary(fire)
```
